---
title: "Shiny_Practice"
author: "Greg"
date: "2023-07-01"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/gregorylederer/Desktop/23-24 Practice Shiny")
```

#packages

```{r}
library(gt)
library(cowplot)
library(ggpubr)
library(dplyr)
library(gtExtras)
library(shiny)
library(shinythemes)
library(gtsummary)
library(htmltools)
library(paletteer)
library(scales)
library(shinydashboard)
library(shinyjs)
library(ggsci)
library(shinyWidgets)
library(here)
library(rsconnect)
```

#get data and file names
```{r}
data <- read.csv("/Users/gregorylederer/Desktop/UMass Basketball/CodeStatSheet - Sheet1.csv")
save_name1 <- paste0(format(Sys.Date(), format = "%Y-%m-%d"), ' | Complete Practice Totals.rds')
save_name2 <- paste0(format(Sys.Date(), format = "%Y-%m-%d"), ' | Basic Practice Totals.rds')
```
#inputs

```{r}
table_subtitle <- paste0(format(Sys.Date(), format="%B %d, %Y"), " | Complete Totals")
```

#full data

```{r}
data[is.na(data)] = 0

full_practice_data <- data %>%
  mutate(Rim_Per = round(Rim_Make/(Rim_Make+Rim_Miss)*100, 1),
         Mid_Per = round(Mid_Make/(Mid_Make+Mid_Miss)*100, 1),
         Three_Per = round(Three_Make/(Three_Make+Three_Miss)*100,1),
         Rim = paste0(Rim_Make, "/", Rim_Make+Rim_Miss),
         Mid = paste0(Mid_Make, "/", Mid_Make+Mid_Miss),
         Three = paste0(Three_Make, "/", Three_Make+Three_Miss),
         Reb = Off_Reb+Def_Reb) %>%
  select(url, Player, Pts, Reb, Ast, Rim, Rim_Per, Mid, Mid_Per, Three, Three_Per, Off_Reb, Def_Reb, Stl, Blk, Tov, Charges, Fouls)

full_practice_data[is.na(full_practice_data)] = 0
```

#full totals row

```{r}
totals_row <- c('https://upload.wikimedia.org/wikipedia/commons/thumb/2/23/UMass_Amherst_athletics_logo.svg/1200px-UMass_Amherst_athletics_logo.svg.png',
                "Totals",
                sum(data$Pts),
                sum(data$Off_Reb)+sum(data$Def_Reb),
                sum(data$Ast),
                paste0(sum(data$Rim_Make), "/", sum(data$Rim_Make)+sum(data$Rim_Miss)),
                round(sum(data$Rim_Make)/(sum(data$Rim_Make)+sum(data$Rim_Miss))*100,1),
                paste0(sum(data$Mid_Make), "/", sum(data$Mid_Make)+sum(data$Mid_Miss)),
                round(sum(data$Mid_Make)/(sum(data$Mid_Make)+sum(data$Mid_Miss))*100,1),
                paste0(sum(data$Three_Make), "/", sum(data$Three_Make)+sum(data$Three_Miss)),
                round(sum(data$Three_Make)/(sum(data$Three_Make)+sum(data$Three_Miss))*100,1),
                sum(data$Off_Reb),
                sum(data$Def_Reb),
                sum(data$Stl),
                sum(data$Blk),
                sum(data$Tov),
                sum(data$Charges),
                sum(data$Fouls)
                )
full_practice_data[nrow(full_practice_data) + 1,] <- totals_row

full_practice_data$Rim_Per = as.numeric(as.character(full_practice_data$Rim_Per))
full_practice_data$Mid_Per = as.numeric(as.character(full_practice_data$Mid_Per))
full_practice_data$Three_Per = as.numeric(as.character(full_practice_data$Three_Per))
```

#basic practice data

```{r}
basic_practice_data <- data %>%
  mutate(Two = paste0(Rim_Make+Mid_Make, "/", Rim_Make+Rim_Miss+Mid_Make+Mid_Miss),
         Two_Per = round((Rim_Make+Mid_Make)/(Rim_Make+Rim_Miss+Mid_Make+Mid_Miss)*100,1),
         Reb = Off_Reb+Def_Reb,
         Three_Per = round(Three_Make/(Three_Make+Three_Miss)*100,1),
         Three = paste0(Three_Make, "/", Three_Make+Three_Miss),
         ) %>%
  select(url, Player, Pts, Reb, Ast, Two, Two_Per, Three, Three_Per, Off_Reb, Def_Reb, Stl, Blk, Tov, Fouls)

basic_practice_data[is.na(basic_practice_data)] <- 0
```

#basic totals row

```{r}
totals_row <- c('https://upload.wikimedia.org/wikipedia/commons/thumb/2/23/UMass_Amherst_athletics_logo.svg/1200px-UMass_Amherst_athletics_logo.svg.png', "Totals", 
                sum(basic_practice_data$Pts), 
                sum(data$Off_Reb)+sum(data$Def_Reb), 
                sum(basic_practice_data$Ast), 
                paste0(sum(data$Rim_Make)+sum(data$Mid_Make), "/", sum(data$Rim_Make)+sum(data$Mid_Make)+sum(data$Rim_Miss)+sum(data$Mid_Miss)),
                round((sum(data$Rim_Make)+sum(data$Mid_Make))/(sum(data$Rim_Make)+sum(data$Mid_Make)+sum(data$Rim_Miss)+sum(data$Mid_Miss))*100,1),
                paste0(sum(data$Three_Make), "/", sum(data$Three_Make)+sum(data$Three_Miss)),
                round(sum(data$Three_Make)/(sum(data$Three_Make)+sum(data$Three_Miss))*100,1),
                sum(basic_practice_data$Off_Reb), 
                sum(basic_practice_data$Def_Reb), 
                sum(basic_practice_data$Stl), 
                sum(basic_practice_data$Blk), 
                sum(basic_practice_data$Tov), 
                sum(basic_practice_data$Fouls)
                )
basic_practice_data[nrow(basic_practice_data) + 1,] <- totals_row
```

#full practice table

```{r}
full_practice_table <- full_practice_data %>%
  gt() %>%
  gt_theme_538() %>%
  gt_highlight_rows(rows = c(2, 4, 6, 8, 10, 12, 14), fill = 'gray94', font_weight = 'normal', font_color = 'gray30') %>%
  gt_highlight_rows(rows = c(16), fill = 'gray77') %>%
  cols_label(url = '', Player = md('**Player**'), Pts = md('**Pts**'), Rim = md('**Rim**'), Rim_Per = md('**Rim%**'), Mid = md('**Mid**'), Mid_Per = md('**Mid%**'), Three = md('**3pt.**'), Three_Per = md('**3pt%**'), Off_Reb = md('**OReb**'), Def_Reb = md('**DReb**'), Reb = md('**Reb**'), Ast = md('**Ast**'), Stl = md('**Stl**'), Blk = md('**Blk**'), Tov = md('**Tov**'), Charges = md('**Charges**'), Fouls = md('**Fouls**')) %>%
  tab_header(title = md('**Practice Stat Sheet**'), subtitle = table_subtitle) %>%
  text_transform(locations = cells_body(vars(url)), fn = function(x) {web_image(url = x, height = px(22.5))}) %>%
  data_color(columns = c(Rim_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = NULL)) %>%
  data_color(columns = c(Mid_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = NULL)) %>%
  data_color(columns = c(Three_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = NULL)) %>%
  tab_options(table.background.color = 'gray89', heading.background.color = 'gray89', column_labels.background.color = 'gray89') %>%
  tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15) %>%
  gt_add_divider(Ast) %>%
  gt_add_divider(Rim_Per) %>%
  gt_add_divider(Mid_Per) %>%
  gt_add_divider(Three_Per) %>%
  tab_options(column_labels.font.size = 13) %>%
  cols_align(align = c('center'), columns = vars(Pts, Reb, Ast, Rim, Rim_Per, Mid, Mid_Per, Three, Three_Per, Off_Reb, Def_Reb, Stl, Blk, Tov, Charges, Fouls)) %>%
  sub_missing() %>%
  opt_interactive(use_compact_mode = TRUE)
saveRDS(full_practice_table, file = save_name1)
```

#basic practice table

```{r}
basic_practice_table <- basic_practice_data %>%
  gt() %>%
  gt_theme_538() %>%
  gt_highlight_rows(rows = c(2, 4, 6, 8, 10, 12, 14), fill = 'gray94', font_weight = 'normal', font_color = 'gray30') %>%
  gt_highlight_rows(rows = c(16), fill = 'gray77') %>%
  cols_label(url = '', Player = md('**Player**'), Pts = md('**Pts**'), Two = md('**2pt.**'), Two_Per = md('**2pt%**'), Three = md('**3pt.**'), Three_Per = md('**3pt%**'), Off_Reb = md('**OReb**'), Def_Reb = md('**DReb**'), Reb = md('**Reb**'), Ast = md('**Ast**'), Stl = md('**Stl**'), Blk = md('**Blk**'), Tov = md('**Tov**'), Fouls = md('**Fouls**')) %>%
  tab_header(title = md('**Practice Stat Sheet**'), subtitle = table_subtitle) %>%
  text_transform(locations = cells_body(vars(url)), fn = function(x) {web_image(url = x, height = px(22.5))}) %>%
  tab_options(table.background.color = 'gray89', heading.background.color = 'gray89', column_labels.background.color = 'gray89') %>%
  tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15) %>%
  cols_align(align = c('center'), columns = vars(Pts, Two, Two_Per, Three, Three_Per, Off_Reb, Def_Reb, Reb, Ast, Stl, Blk, Tov, Fouls)) %>%
  gt_add_divider(Ast) %>%
  gt_add_divider(Two_Per) %>%
  gt_add_divider(Three_Per) %>%
  sub_missing() %>%
  opt_interactive(use_compact_mode = TRUE)
saveRDS(basic_practice_table, file = save_name2)
```

#shiny input date
```{r, shinyapp}
ui <- fluidPage(
  tags$head(
    tags$style(
      HTML("
        body {background-color: #7A1717;}
        .custom-title-panel {color: #FFFFFF;}
        .custom-sidebar-panel {background-color: #E3E3E3;}
        .custom-sidebar-text {color: #000000;}
        .my-tabpanel {
          font-size: 20px;
          height: 800px;
        }
        .navbar {background-color: #E3E3E3;}
        .navbar .nav > li > a {
          color: #000000;
          font-size: 20px;
          font-weight: bold;
        }")
    )
  ),
  navbarPage(
    title = "",
    tabPanel(
      "UMass MBB Practice",
      class = "my-tabpanel",
      mainPanel(
        img(src = 'https://pbs.twimg.com/media/FyNTeg8XwAA0hIW?format=jpg&name=medium', align = 'left')
      )
    ),
    tabPanel(
      "Daily Tables",
      class = "my-tabpanel",
      sidebarLayout(
        sidebarPanel(
          class = "custom-sidebar-panel",
          div(
            dateInput("selectedDate", "Select Date:", value = Sys.Date()),
            class = "custom-sidebar-text",
            p('Complete Totals and Basic Totals below')
          )
        ),
        mainPanel(
          gt_output("playerStatsTable"),
          gt_output("playerStatsTable2")
        )
      )
    )
  )
)

server <- function(input, output) {
  observeEvent(input$selectedDate, {
    selected_date <- input$selectedDate
    file_name <- paste0(format(selected_date, "%Y-%m-%d"), ' | Complete Practice Totals.rds')
    file_name2 <- paste0(format(selected_date, "%Y-%m-%d"), ' | Basic Practice Totals.rds')
    
    if (file.exists(file_name)) {
      tbl <- data.frame(readRDS(file = file_name))
      output$playerStatsTable <- render_gt({
        tbl$Rim_Per <- suppressWarnings(as.numeric(tbl$Rim_Per))
        tbl$Mid_Per <- suppressWarnings(as.numeric(tbl$Mid_Per))
        tbl$Three_Per <- suppressWarnings(as.numeric(tbl$Three_Per))
        tbl$url <- full_practice_data$url
        column_averages_rim <- sapply(tbl[, c("Rim_Per")], mean)
        column_averages_mid <- sapply(tbl[, c("Mid_Per")], mean)
        column_averages_three <- sapply(tbl[, c("Three_Per")], mean)
        
        tbl %>%
          gt() %>%
          gt_theme_538() %>%
          tab_style(style = list(cell_fill(color = "gray80")), locations = cells_body(rows = seq(1, nrow(tbl), by = 2))) %>%
          tab_style(style = list(cell_fill(color = "gray70")), locations = cells_body(rows = nrow(tbl))) %>%
          cols_label(url = '', Player = md('**Player**'), Pts = md('**Pts**'), Rim = md('**Rim**'), Rim_Per = md('**Rim%**'), Mid = md('**Mid**'), Mid_Per = md('**Mid%**'), Three = md('**3pt.**'), Three_Per = md('**3pt%**'), Off_Reb = md('**OReb**'), Def_Reb = md('**DReb**'), Reb = md('**Reb**'), Ast = md('**Ast**'), Stl = md('**Stl**'), Blk = md('**Blk**'), Tov = md('**Tov**'), Charges = md('**Charges**'), Fouls = md('**Fouls**')) %>%
          tab_header(title = md('**Practice Stat Sheet**'), subtitle = paste0(format(selected_date, "%A, %B %d, %Y"), ' | Complete Totals')) %>%
          text_transform(locations = cells_body(vars(url)), fn = function(x) {web_image(url = x, height = px(22.5))}) %>%
          data_color(columns = c(Rim_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = column_averages_rim)) %>%
          data_color(columns = c(Mid_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = column_averages_mid)) %>%
          data_color(columns = c(Three_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = column_averages_three)) %>%
          tab_options(table.background.color = 'gray89', heading.background.color = 'gray89', column_labels.background.color = 'gray89') %>%
          tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15) %>%
          gt_add_divider(Ast) %>%
          gt_add_divider(Rim_Per) %>%
          gt_add_divider(Mid_Per) %>%
          gt_add_divider(Three_Per) %>%
          tab_options(column_labels.font.size = 13) %>%
          cols_align(align = c('center'), columns = c(Pts, Reb, Ast, Rim, Rim_Per, Mid, Mid_Per, Three, Three_Per, Off_Reb, Def_Reb, Stl, Blk, Tov, Charges, Fouls))
      })
      
    } else {
      output$playerStatsTable <- render_gt({
        empty_tbl <- data.frame(Placeholder = character(0))
        gt(empty_tbl) %>%
          cols_hide(columns = vars(everything())) %>%
          tab_header(title = md('**Practice Stat Sheet**'), subtitle = "No stats available for the selected date.") %>%
          tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15) %>%
          tab_options(table.background.color = '#7A1717', heading.background.color = '#7A1717', column_labels.background.color = '#7A1717')
      })
    }
    
    if (file.exists(file_name2)) {
      tbl2 <- data.frame(readRDS(file = file_name2))
      output$playerStatsTable2 <- render_gt({
        tbl2$url <- full_practice_data$url
        tbl2 %>%
          gt() %>%
          gt_theme_538() %>%
          tab_style(style = list(cell_fill(color = "gray80")), locations = cells_body(rows = seq(1, nrow(tbl), by = 2))) %>%
          tab_style(style = list(cell_fill(color = "gray70")), locations = cells_body(rows = nrow(tbl))) %>%
          cols_label(url = '', Player = md('**Player**'), Pts = md('**Pts**'), Two = md('**2pt.**'), Two_Per = md('**2pt%**'), Three = md('**3pt.**'), Three_Per = md('**3pt%**'), Off_Reb = md('**OReb**'), Def_Reb = md('**DReb**'), Reb = md('**Reb**'), Ast = md('**Ast**'), Stl = md('**Stl**'), Blk = md('**Blk**'), Tov = md('**Tov**'), Fouls = md('**Fouls**')) %>%
          tab_header(title = md('**Practice Stat Sheet**'), subtitle = paste0(format(selected_date, "%A, %B %d, %Y"), ' | Basic Totals')) %>%
          text_transform(locations = cells_body(vars(url)), fn = function(x) {web_image(url = x, height = px(22.5))}) %>%
          tab_options(table.background.color = 'gray89', heading.background.color = 'gray89', column_labels.background.color = 'gray89') %>%
          tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15) %>%
          cols_align(align = c('center'), columns = vars(Pts, Two, Two_Per, Three, Three_Per, Off_Reb, Def_Reb, Reb, Ast, Stl, Blk, Tov, Fouls)) %>%
          gt_add_divider(Ast) %>%
          gt_add_divider(Two_Per) %>%
          gt_add_divider(Three_Per)
      })
    } else {
      output$playerStatsTable2 <- render_gt({
        empty_tbl <- data.frame(Placeholder = character(0))
        gt(empty_tbl) %>%
          cols_hide(columns = vars(everything()))
          # tab_header(title = md('**Practice Stat Sheet**'), subtitle = "No stats available for the selected date.") %>%
          # tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15)
      })
    }
  })
}

shinyApp(ui = ui, server = server)

rsconnect::setAccountInfo(name='gregorylederer', token='30FACEC779D6F378ACF290984B48B571', secret='GRZ8S4SFstz7aiqMgz+uCmaJoLp38wLKdk1IIBvS')
rsconnect::deployApp(appDir = ".", appName = "PracticeStats23-24")
```


#all good 
ui <- fluidPage(
  tags$head(
    tags$style(
      HTML("
        body {background-color: #7A1717;}
        .custom-title-panel {color: #FFFFFF;}
        .custom-sidebar-panel {background-color: #E3E3E3;}
        .custom-sidebar-text {color: #000000;}
        .my-tabpanel {
          font-size: 20px;
          height: 800px;
        }
        .navbar {background-color: #E3E3E3;}
        .navbar .nav > li > a {
          color: #000000;
          font-size: 20px;
          font-weight: bold;
        }")
    )
  ),
  navbarPage(
    title = "",
    tabPanel(
      "UMass MBB Practice",
      class = "my-tabpanel",
      mainPanel(
        img(src = 'https://pbs.twimg.com/media/FyNTeg8XwAA0hIW?format=jpg&name=medium', align = 'left')
      )
    ),
    tabPanel(
      "Daily Tables",
      class = "my-tabpanel",
      sidebarLayout(
        sidebarPanel(
          class = "custom-sidebar-panel",
          div(
            dateInput("selectedDate", "Select Date:", value = Sys.Date()),
            class = "custom-sidebar-text",
            p('Complete Totals and Basic Totals below')
          )
        ),
        mainPanel(
          gt_output("playerStatsTable"),
          gt_output("playerStatsTable2")
        )
      )
    )
  )
)

server <- function(input, output) {
  observeEvent(input$selectedDate, {
    selected_date <- input$selectedDate
    file_name <- paste0(format(selected_date, "%Y-%m-%d"), ' | Complete Practice Totals.rds')
    file_name2 <- paste0(format(selected_date, "%Y-%m-%d"), ' | Basic Practice Totals.rds')
    
    if (file.exists(file_name)) {
      tbl <- data.frame(readRDS(file = file_name))
      output$playerStatsTable <- render_gt({
        tbl$Rim_Per <- suppressWarnings(as.numeric(tbl$Rim_Per))
        tbl$Mid_Per <- suppressWarnings(as.numeric(tbl$Mid_Per))
        tbl$Three_Per <- suppressWarnings(as.numeric(tbl$Three_Per))
        tbl$url <- full_practice_data$url
        column_averages_rim <- sapply(tbl[, c("Rim_Per")], mean)
        column_averages_mid <- sapply(tbl[, c("Mid_Per")], mean)
        column_averages_three <- sapply(tbl[, c("Three_Per")], mean)
        
        tbl %>%
          gt() %>%
          gt_theme_538() %>%
          tab_style(style = list(cell_fill(color = "gray80")), locations = cells_body(rows = seq(1, nrow(tbl), by = 2))) %>%
          tab_style(style = list(cell_fill(color = "gray70")), locations = cells_body(rows = nrow(tbl))) %>%
          cols_label(url = '', Player = md('**Player**'), Pts = md('**Pts**'), Rim = md('**Rim**'), Rim_Per = md('**Rim%**'), Mid = md('**Mid**'), Mid_Per = md('**Mid%**'), Three = md('**3pt.**'), Three_Per = md('**3pt%**'), Off_Reb = md('**OReb**'), Def_Reb = md('**DReb**'), Reb = md('**Reb**'), Ast = md('**Ast**'), Stl = md('**Stl**'), Blk = md('**Blk**'), Tov = md('**Tov**'), Charges = md('**Charges**'), Fouls = md('**Fouls**')) %>%
          tab_header(title = md('**Practice Stat Sheet**'), subtitle = paste0(format(selected_date, "%A, %B %d, %Y"), ' | Complete Totals')) %>%
          text_transform(locations = cells_body(vars(url)), fn = function(x) {web_image(url = x, height = px(22.5))}) %>%
          data_color(columns = c(Rim_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = column_averages_rim)) %>%
          data_color(columns = c(Mid_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = column_averages_mid)) %>%
          data_color(columns = c(Three_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = column_averages_three)) %>%
          tab_options(table.background.color = 'gray89', heading.background.color = 'gray89', column_labels.background.color = 'gray89') %>%
          tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15) %>%
          gt_add_divider(Ast) %>%
          gt_add_divider(Rim_Per) %>%
          gt_add_divider(Mid_Per) %>%
          gt_add_divider(Three_Per) %>%
          tab_options(column_labels.font.size = 13) %>%
          cols_align(align = c('center'), columns = c(Pts, Reb, Ast, Rim, Rim_Per, Mid, Mid_Per, Three, Three_Per, Off_Reb, Def_Reb, Stl, Blk, Tov, Charges, Fouls))
      })
      
    } else {
      output$playerStatsTable <- render_gt({
        empty_tbl <- data.frame(Placeholder = character(0))
        gt(empty_tbl) %>%
          cols_hide(columns = vars(everything())) %>%
          tab_header(title = md('**Practice Stat Sheet**'), subtitle = "No stats available for the selected date.") %>%
          tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15) %>%
          tab_options(table.background.color = '#7A1717', heading.background.color = '#7A1717', column_labels.background.color = '#7A1717')
      })
    }
    
    if (file.exists(file_name2)) {
      tbl2 <- data.frame(readRDS(file = file_name2))
      output$playerStatsTable2 <- render_gt({
        tbl2$url <- full_practice_data$url
        tbl2 %>%
          gt() %>%
          gt_theme_538() %>%
          tab_style(style = list(cell_fill(color = "gray80")), locations = cells_body(rows = seq(1, nrow(tbl), by = 2))) %>%
          tab_style(style = list(cell_fill(color = "gray70")), locations = cells_body(rows = nrow(tbl))) %>%
          cols_label(url = '', Player = md('**Player**'), Pts = md('**Pts**'), Two = md('**2pt.**'), Two_Per = md('**2pt%**'), Three = md('**3pt.**'), Three_Per = md('**3pt%**'), Off_Reb = md('**OReb**'), Def_Reb = md('**DReb**'), Reb = md('**Reb**'), Ast = md('**Ast**'), Stl = md('**Stl**'), Blk = md('**Blk**'), Tov = md('**Tov**'), Fouls = md('**Fouls**')) %>%
          tab_header(title = md('**Practice Stat Sheet**'), subtitle = paste0(format(selected_date, "%A, %B %d, %Y"), ' | Basic Totals')) %>%
          text_transform(locations = cells_body(vars(url)), fn = function(x) {web_image(url = x, height = px(22.5))}) %>%
          tab_options(table.background.color = 'gray89', heading.background.color = 'gray89', column_labels.background.color = 'gray89') %>%
          tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15) %>%
          cols_align(align = c('center'), columns = vars(Pts, Two, Two_Per, Three, Three_Per, Off_Reb, Def_Reb, Reb, Ast, Stl, Blk, Tov, Fouls)) %>%
          gt_add_divider(Ast) %>%
          gt_add_divider(Two_Per) %>%
          gt_add_divider(Three_Per)
      })
    } else {
      output$playerStatsTable2 <- render_gt({
        empty_tbl <- data.frame(Placeholder = character(0))
        gt(empty_tbl) %>%
          cols_hide(columns = vars(everything()))
          # tab_header(title = md('**Practice Stat Sheet**'), subtitle = "No stats available for the selected date.") %>%
          # tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15)
      })
    }
  })
}

shinyApp(ui = ui, server = server) 

#good player input 
ui \<- fluidPage(
titlePanel("Player Stats"), sidebarLayout( sidebarPanel(
selectInput("player", "Select Player:", choices =
unique(full_practice_data\$Player)) ), mainPanel(
gt_output("playerStatsTable") ) ) )

server \<- function(input, output) {
output$playerStatsTable <- render_gt({ selected_player <- input$player
player_stats \<- subset(full_practice_data, Player == selected_player)

```         
column_averages <- sapply(player_stats[, c("Rim_Per", "Mid_Per", "Three_Per")], mean)

tbl <- gt(player_stats) %>%
  gt_theme_538() %>%
  gt_highlight_rows(rows = c(2, 4, 6, 8, 10, 12, 14), fill = 'gray94', font_weight = 'normal', font_color = 'gray30') %>%
  gt_highlight_rows(rows = c(16), fill = 'gray77') %>%
  cols_label(url = '', Player = md('**Player**'), Pts = md('**Pts**'), Rim = md('**Rim**'), Rim_Per = md('**Rim%**'), Mid = md('**Mid**'), Mid_Per = md('**Mid%**'), Three = md('**3pt.**'), Three_Per = md('**3pt%**'), Off_Reb = md('**OReb**'), Def_Reb = md('**DReb**'), Reb = md('**Reb**'), Ast = md('**Ast**'), Stl = md('**Stl**'), Blk = md('**Blk**'), Tov = md('**Tov**'), Charges = md('**Charges**'), Fouls = md('**Fouls**')) %>%
  tab_header(title = md('**Practice Stat Sheet**'), subtitle = table_subtitle) %>%
  text_transform(locations = cells_body(vars(url)), fn = function(x) {web_image(url = x, height = px(22.5))}) %>%
  data_color(columns = c(Rim_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = column_averages)) %>%
  data_color(columns = c(Mid_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = column_averages)) %>%
  data_color(columns = c(Three_Per), colors = scales::col_numeric(palette = paletteer::paletteer_d(palette = "ggsci::green_material") %>% as.character(), domain = column_averages)) %>%
  tab_options(table.background.color = 'gray89', heading.background.color = 'gray89', column_labels.background.color = 'gray89') %>%
  tab_options(heading.title.font.size = 30, heading.subtitle.font.size = 15) %>%
  gt_add_divider(Ast) %>%
  gt_add_divider(Rim_Per) %>%
  gt_add_divider(Mid_Per) %>%
  gt_add_divider(Three_Per) %>%
  tab_options(column_labels.font.size = 13) %>%
  cols_align(align = c('center'), columns = vars(Pts, Reb, Ast, Rim, Rim_Per, Mid, Mid_Per, Three, Three_Per, Off_Reb, Def_Reb, Stl, Blk, Tov, Charges, Fouls)) 
```

}) }

shinyApp(ui = ui, server = server)